Software Citation Principles

### 2016-04-05 sc-principles/software-citation-principles.tex
undoing one SCTC change in section 1

\item \textbf{Credit and Attribution}: \label{principle:credit}
Software citations should facilitate giving scholarly credits and normative
and legal attribution to all contributors to the software, recognizing
that a single style or mechanism of attribution may not be applicable to
all software.

>>>>

\item \textbf{Credit and Attribution}: \label{principle:credit}
Software citations should facilitate giving scholarly credit and normative
and legal attribution to all contributors to the software, recognizing
that a single style or mechanism of attribution may not be applicable to
all software.
